FoRTE baseline

### 2019-10-11 analysis/paper/paper.Rmd
Add PFT LAI figure and update related text

```{r pairs-time, fig.cap = pairs_time_cap}
pairs_time_cap <- paste(
  htmlfig(),
  "ED2 predictions of annual mean NPP and growing-season LAI in 1920, 1950, and 1999",
  "by model type.",
  "Each point indicates a single ensemble run with a different set of parameters.",
  "Solid line is the best-fit generalized additive model (GAM).",
  "Dashed lines indicate the error bounds of present-day observed NPP and LAI."
)
readd(npp_lai_pairs_knit)
```

@@

```{r bigfacet-plot, fig.cap = bigfacet_cap}
bigfacet_cap <- paste(
  htmlfig(),
  "PFT-level predictions of leaf area index (LAI) by model configuration and parameterization.",
  "Each row of plots is a simulation with the same set of parameters across model configurations.",
  "Letters correspond to the labels in Figure 3.",
  "Note that these are predictions of total leaf area index summed across all cohorts of the same PFT,",
  "meaning that higher LAI in one PFT does not necessarily indicate dominance, size, etc."
)
readd(lai_pft_plot_knit)
```

`r mdcap(bigfacet_cap)`

Model structure and parameters interacted to determine the community assembly and dynamics of each simulation, with consequences for overall ecosystem productivity that varied by model structure (Figure 4).
Consider simulations **A** and **C**, the former showing competition of early hardwood with pine, and the latter completely dominated by pine:
With a closed canopy and static traits, both simulations produced similar overall LAI and NPP values (Figure 3), but moving to a finite canopy dramatically increased the total LAI in **C** without much affecting **A**, while enabling trait plasticity dramatically increased the NPP of **A** without much affecting **C** (Figure 3).
This example also shows the impacts of different configurations on predicted community dynamics -- namely, in this specific case, enabling trait plasticity helped pine out-perform early hardwood, but only under a closed (rather than finite) canopy.
Finite canopy radius similarly benefits early hardwood in its competition against late hardwood in simulations **B** and, to a lesser extent, **D**.
Simulations **B** and **D** also show that the sensitivity of a given parameter combination to model structure is itself dependent on the parameters -- simulation **B** produced similar ecological dynamics and aggregate state variables regardless of model configuration (except the extreme cases; Figure 3), while simulation **D** had near-zero NPP and LAI in two cases (closed, two-stream, static and finite, multi-scatter, plastic), comparable NPP and LAI to **B** with closed canopy and trait plasticity, and higher NPP and LAI than **D** with a finite canopy, multi-scatter radiative transfer, and static traits (Figure 3).

>>>>

```{r pairs-time, fig.cap = pairs_time_cap}
pairs_time_cap <- paste(
  htmlfig(),
  "ED2 predictions of annual mean NPP and growing-season LAI in 1920, 1950, and 1999",
  "by model type.",
  "Each point indicates a single ensemble run with a different set of parameters.",
  "Solid line is the best-fit generalized additive model (GAM).",
  "Dashed lines indicate the error bounds of present-day observed NPP and LAI.",
  "Text labels match the rows in Figure X below."
)
readd(npp_lai_pairs_knit)
```

@@

```{r lai-pft-plot, fig.cap = lai_pft_cap}
lai_pft_cap <- paste(
  htmlfig(),
  "PFT-level predictions of leaf area index (LAI) by model configuration and parameterization.",
  "Each row of plots is a simulation with the same set of parameters across model configurations.",
  "Letters correspond to the labels in Figure 3.",
  "Note that these are predictions of total leaf area index summed across all cohorts of the same PFT,",
  "meaning that higher LAI in one PFT does not necessarily indicate dominance, size, etc."
)
readd(lai_pft_plot_knit)
```

Model structure and parameters interacted to determine the community assembly and dynamics of each simulation, with consequences for overall ecosystem productivity that varied by model structure (Figure X).
Parameter sets **A** and **B** both resulted in similar patterns of immediate and complete dominance by mid- and late-hardwood, respectively, followed by gradual decline to near-zero LAI.
In both of these simulations, peak productivity was higher and was sustained for longer when the canopy was closed rather than finite, and this difference was larger under a two-stream rather than a multiple-scatter radiative transfer model.
Trait plasticity had relatively little effect on most of these two simulations, though in parameter set **B**, under the combination of closed canopy, multiple-scatter radiative transfer, and plastic traits, pine overtook the dominant late hardwood PFT starting around 1975.
Both of these parameter sets also had the lowest LAI of the five selected here, with a peak LAI of 1 in **A** and 2 in **B**.
Parameter set **C** showed much more variety in compositional dynamics with model structure:
In all cases, mid-hardwoods began as the dominant species and were eventually overtaken by pine under a closed canopy and plastic traits, or early hardwood in all other cases (though with a closed canopy and static traits, the final LAI was low).
Parameter sets **D** and **E** had the highest productivity of these five sets, and were characterized by strong dominance of Early Hardwood and Pine, respectively.
